Carbonate chemistry at Ny-Ålesund: AWIPEV-CO~2~ Project

### 2020-05-22 awipev-CO2.Rmd
continue debugging

#create new variable in "discrete_is_na" to bind "discrete_no_na"
discrete_is_na$phcalc_insitu <- NA
discrete_no_na$pco2_calc_insitu <- NA
discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
  dplyr::arrange(date)

@@

```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE}
title <- "Contros vs calculated pCO2"
fit <- lmodel2(data = d_all,  pco2_corr ~ pco2_calc , nperm = 99)

p <-  ggplot(d_all,aes(x=pco2_calc, y= pco2_corr, label = month))+
   geom_text(aes(color = factor(month)))+
  scale_color_discrete(guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
  labs(x="Calculated pCO2", y="Contros pCO2 corrected", color = "Months") + theme_bw()  
```
The relationship between the Contros and calculated *p*CO~2~ is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
print(p) # pco2_calc_pco2_corr_text
```

@@

```{r Final pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
pco2_contros_xts <-
  dplyr::select(d_all, datetime, pco2_calc, pco2_corr)
pco2_contros_xts <-
  as.xts(pco2_contros_xts, order.by = d_all$datetime)
dygraph(pco2_contros_xts,
        group = "awipev",
        main = "<i>p</i>CO<sub>2</sub>",
        ylab = "<i>p</i>CO<sub>2</sub>") %>%
  dySeries(
    "pco2_corr",
    label = "Corrected pCO2",
    color =  RColorBrewer::brewer.pal(3, "Dark2")[1],
    strokeWidth = 0,
    pointSize = 2
  ) %>%
  dySeries(
    "pco2_calc",
    label = "pco2_calc",
    color = "red",
    strokeWidth = 0,
    pointSize = 4
  ) %>%
  dyEvent(
    as.POSIXct("2016-02-28 12:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2017-02-07 12:00:00", tz = "UTC"),
    "CO2FT-0215-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2018-04-16 12:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2018-10-31 15:00:00", tz = "UTC"),
    "CO2FT-0215-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2019-09-03 15:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyHighlight(
    highlightCircleSize = 8,
    highlightSeriesBackgroundAlpha = 0.5,
    hideOnMouseOut = TRUE
  ) %>%
  dyLegend(show = "follow")   %>%
  dyOptions(
    drawGrid = TRUE,
    drawPoints = TRUE,
    pointSize = c(1, 8, 1),
    useDataTimezone = TRUE
  ) %>%
  dyRangeSelector(height = 30, dateWindow = NULL)

@@

#periode 1, mean of 4 next hours for volt int + T seaF
# mean_voltINT_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
#       datetime <= as.POSIXct("2017-08-24 22:00:00")
#   ) %>%
#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
#mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-08-24 19:00:00") &
      datetime <= as.POSIXct("2017-08-24 22:00:00")
  )
mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltINT = ifelse(
    datetime == as.POSIXct("2017-08-24 13:00:00"),
    mean_voltINT_4h,
    voltINT
  ))
# mean_voltEXT_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
#       datetime <= as.POSIXct("2017-08-24 22:00:00")
#   ) %>%
#   dplyr::summarise(mean(voltEXT, na.rm = TRUE))
# mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-08-24 19:00:00") &
      datetime <= as.POSIXct("2017-08-24 22:00:00")
  )
mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltEXT = ifelse(
    datetime == as.POSIXct("2017-08-24 13:00:00"),
    mean_voltEXT_4h,
    voltEXT
  ))
# mean_TseaF_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
#       datetime <= as.POSIXct("2017-08-24 22:00:00")
#   ) %>%
#   dplyr::summarise(mean(temp_sf, na.rm = TRUE))
# mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-08-24 19:00:00") &
      datetime <= as.POSIXct("2017-08-24 22:00:00")
  )
mean_TseaF_4h <-  mean(zz$temp_sf, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(
    datetime == as.POSIXct("2017-08-24 13:00:00"),
    mean_TseaF_4h,
    temp_mix
  ))

@@

####
## calculation of E0INT25/E0EXT25 ##
##     new sf_calib function      ##
####
calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_insi, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd_interp)
# put number of deployment 
calib_spectro$deployment_sf <- d_all$deployment_sf

@@

#### plot
kk <- melt(calib_spectro, id.vars="deployment_sf")
p_calib <- ggplot(kk) + geom_point(aes(x=deployment_sf, y=value, color=variable),size=2) +
  facet_grid(variable~., scales="free_y") + theme_bw() +
  scale_colour_discrete(guide="none")
print(p_calib)
```

@@

### **Calculated / Durafet pHs**
```{r pHs comparaison dur calc, echo=FALSE, message= FALSE, warning=FALSE}
# Normalize phcalc from AT/CT to 4°c
pH_calc <- discrete %>%
  dplyr::select(datetime, sal_fb, temp_fb, phcalc, at)%>%
  dplyr::filter(!is.na(phcalc), !is.na(temp_fb), !is.na(sal_fb))
pH_calc$pH_calc_norm4 <- pHinsi(pH=pH_calc$phcalc, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp_fb, Pinsi=11/10, S=pH_calc$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

# join pH calc norm + pH dur/sf norm in d_all
d_all <- left_join(d_all, pH_calc%>%dplyr::select(datetime,pH_calc_norm4), by="datetime")

durafet_calc_contros_xts <- dplyr::select(d_all, datetime, pH_durafet_norm4, pH_calc_norm4)
durafet_calc_contros_xts <- as.xts(durafet_calc_contros_xts, order.by = d_all$datetime)
dygraph(durafet_calc_contros_xts, group = "awipev", main="pH calculated vs pH durafet, normalized at 4°C", ylab="pHT") %>%
    dySeries("pH_durafet_norm4", label = "pH durafet", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_calc_norm4", label = "pH calculated", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
       dyLegend(show = "follow")   %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)
```

### **Calculated / seaFET pHs**
```{r pHs comparaison sf calc, echo=FALSE, message= FALSE, warning=FALSE}
seafet_calc_contros_xts <- dplyr::select(d_all, datetime, pHint_tot_sf_norm4, pH_calc_norm4)
seafet_calc_contros_xts <- as.xts(seafet_calc_contros_xts, order.by = d_all$datetime)
dygraph(seafet_calc_contros_xts, group = "awipev", main="pH calculated vs pH seaFET, normalized at 4°C", ylab="pHT") %>%
    dySeries("pHint_tot_sf_norm4", label = "pH seaFET", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_calc_norm4", label = "pH calculated", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
       dyLegend(show = "follow")   %>%
dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)
```

@@

#### Script awipev-co2.Rmd which runs locally
* reads locally fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds
* sal_mix: when ferrybox data (sal_fb) are missing, they are replaced by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_9m)
* temp_mix: when data of in situ temperature at 11 m (temp_insitu_11m) are missing, they are replaced by data from the profiling ctd for depths > 8 m
* pco2_calc: pco2 calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
* calibrate seafet pH
    - ph_s_sf_temp_insi: pH spectro seaFET pH insi calculé avec AT interpolée + temp_mix +sal_mix
    - E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_insi (temp 11m + temp_insitu_ctd_9m si trous) + temp CTD 9m + sal CTD 9m (calib seaFET fonction 1)
    - phint_tot_sf: calculé à partir du voltage interne + E0 + temp CTD + sal CTD (calib seaFET fonction 2)
* ph_calc: pH calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
* despike pH seaFET
* calibrate durafet pH
    - ph_s_dur_temp_fb: pH spectro durafet pH insi calculé avec AT interpolée + temp_fb +sal_fb
* Relation at / sal_mix 
* at_calc: calculé from sal_mix
* saves locally d_all.rds which comprises all variables plus those generated in the script

>>>>

#create new variable in "discrete_is_na" to bind "discrete_no_na"
discrete_is_na$phcalc_insitu <- NA
discrete_is_na$pco2_calc_insitu <- NA
discrete <- bind_rows(discrete_no_na, discrete_is_na) %>% 
  dplyr::arrange(date)

@@

```{r measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE}
title <- "Contros vs calculated pCO2"
fit <- lmodel2(data = d_all,  pco2_corr ~ pco2_calc_insitu , nperm = 99)

p <-  ggplot(d_all,aes(x=pco2_calc_insitu, y= pco2_corr, label = month))+
   geom_text(aes(color = factor(month)))+
  scale_color_discrete(guide="none")+
  geom_abline(slope = 1, intercept = 0, linetype = "dashed") +
  geom_abline(aes(intercept = fit$regression.results[2,2], slope = fit$regression.results[2,3]),colour = "blue") +
  labs(title = paste(title,"\n Adj R2 = ", signif(fit$rsquare, 3),
                     "; Intercept =", signif(fit$regression.results[2,2], 3),
                     "; Slope =", signif( fit$regression.results[2,3], 3),
                     "; P =", signif(fit$P.param, 3))) +
  theme(aspect.ratio=1,plot.title = element_text(size=7)) + 
  coord_fixed(ratio = 1 ,xlim=c(200,460) , ylim=c(200,460))+
  labs(x="Calculated pCO2", y="Contros pCO2 corrected", color = "Months") + theme_bw()  
```
The relationship between the Contros and calculated *p*CO~2~ is not good at all in the sense that it is far from the 1:1 line, despite a good r2 (`r round(fit$rsquare, digits=2)`).
```{r plot measured vs calculated pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
print(p) # pco2_calc_insitu_pco2_corr_text
```

@@

```{r Final pCO2, echo=FALSE, warning=FALSE, message=FALSE, out.width='100%', fig.align="center"}
pco2_contros_xts <-
  dplyr::select(d_all, datetime, pco2_calc_insitu, pco2_corr)
pco2_contros_xts <-
  as.xts(pco2_contros_xts, order.by = d_all$datetime)
dygraph(pco2_contros_xts,
        group = "awipev",
        main = "<i>p</i>CO<sub>2</sub>",
        ylab = "<i>p</i>CO<sub>2</sub>") %>%
  dySeries(
    "pco2_corr",
    label = "Corrected pCO2",
    color =  RColorBrewer::brewer.pal(3, "Dark2")[1],
    strokeWidth = 0,
    pointSize = 2
  ) %>%
  dySeries(
    "pco2_calc_insitu",
    label = "pco2_calc_insitu",
    color = "red",
    strokeWidth = 0,
    pointSize = 4
  ) %>%
  dyEvent(
    as.POSIXct("2016-02-28 12:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2017-02-07 12:00:00", tz = "UTC"),
    "CO2FT-0215-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2018-04-16 12:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2018-10-31 15:00:00", tz = "UTC"),
    "CO2FT-0215-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyEvent(
    as.POSIXct("2019-09-03 15:00:00", tz = "UTC"),
    "CO2FT-0515-001 installed",
    labelLoc = "bottom",
    color = "red"
  ) %>%
  dyHighlight(
    highlightCircleSize = 8,
    highlightSeriesBackgroundAlpha = 0.5,
    hideOnMouseOut = TRUE
  ) %>%
  dyLegend(show = "follow")   %>%
  dyOptions(
    drawGrid = TRUE,
    drawPoints = TRUE,
    pointSize = c(1, 8, 1),
    useDataTimezone = TRUE
  ) %>%
  dyRangeSelector(height = 30, dateWindow = NULL)

@@

# $SA$ below
#periode 1, mean of 4 next hours for volt int + T seaF
# mean_voltINT_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
#       datetime <= as.POSIXct("2017-08-24 22:00:00")
#   ) %>%
#   dplyr::summarise(mean(voltINT, na.rm = TRUE))
#mean_voltINT_4h <- as.numeric(mean_voltINT_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-08-24 19:00:00") &
      datetime <= as.POSIXct("2017-08-24 22:00:00")
  )
mean_voltINT_4h <-  mean(zz$voltINT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltINT = ifelse(
    datetime == as.POSIXct("2017-08-24 13:00:00"),
    mean_voltINT_4h,
    voltINT
  ))
# mean_voltEXT_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
#       datetime <= as.POSIXct("2017-08-24 22:00:00")
#   ) %>%
#   dplyr::summarise(mean(voltEXT, na.rm = TRUE))
# mean_voltEXT_4h <- as.numeric(mean_voltEXT_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-08-24 19:00:00") &
      datetime <= as.POSIXct("2017-08-24 22:00:00")
  )
mean_voltEXT_4h <-  mean(zz$voltEXT, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(voltEXT = ifelse(
    datetime == as.POSIXct("2017-08-24 13:00:00"),
    mean_voltEXT_4h,
    voltEXT
  ))
# mean_TseaF_4h <- d_all %>%
#   dplyr::filter(
#     datetime >= as.POSIXct("2017-08-24 19:00:00") &
#       datetime <= as.POSIXct("2017-08-24 22:00:00")
#   ) %>%
#   dplyr::summarise(mean(temp_sf, na.rm = TRUE))
# mean_TseaF_4h <- as.numeric(mean_TseaF_4h)
zz <- d_all %>%
  dplyr::filter(
    datetime >= as.POSIXct("2017-08-24 19:00:00") &
      datetime <= as.POSIXct("2017-08-24 22:00:00")
  )
mean_TseaF_4h <-  mean(zz$temp_sf, na.rm = TRUE)
d_all <- d_all %>%
  dplyr::mutate(temp_mix = ifelse(
    datetime == as.POSIXct("2017-08-24 13:00:00"),
    mean_TseaF_4h,
    temp_mix
  ))

@@

####
## calculation of E0INT25/E0EXT25 ##
##     new sf_calib function      ##
####
calib_spectro <- sf_calib(calEint = d_all$voltINT, calEext = d_all$voltEXT, calpH = d_all$ph_s_sf_temp_insi, calT = d_all$temp_sf, calSal = d_all$sal_insitu_ctd)
# put number of deployment 
calib_spectro$deployment_sf <- d_all$deployment_sf

@@

#### plot
# $SA$ 3 points?
kk <- melt(calib_spectro, id.vars="deployment_sf")
p_calib <- ggplot(kk) + geom_point(aes(x=deployment_sf, y=value, color=variable),size=2) +
  facet_grid(variable~., scales="free_y") + theme_bw() +
  scale_colour_discrete(guide="none")
print(p_calib)
```

@@

### **Calculated / Durafet pHs**
```{r pHs comparaison dur calc, echo=FALSE, message= FALSE, warning=FALSE}
# Normalize phcalc from AT/CT to 4°c
pH_calc <- discrete %>%
  dplyr::select(datetime, sal_fb, temp_fb, phcalc_fb, at)%>%
  dplyr::filter(!is.na(phcalc_fb), !is.na(temp_fb), !is.na(sal_fb))
pH_calc$pH_calc_fb_norm4 <- pHinsi(pH = pH_calc$phcalc_fb, ALK=pH_calc$at*1e-6, Tinsi=4, Tlab=pH_calc$temp_fb, Pinsi=11/10, S=pH_calc$sal_fb, Pt=0, Sit=0, k1k2 = "x", kf = "x", ks="d", pHscale = "T", b="u74")

# join pH calc norm + pH dur/sf norm in d_all
d_all <- left_join(d_all, pH_calc %>% dplyr::select(datetime, pH_calc_fb_norm4), by="datetime")

durafet_calc_contros_xts <- dplyr::select(d_all, datetime, pH_durafet_norm4, pH_calc_fb_norm4)
durafet_calc_contros_xts <- as.xts(durafet_calc_contros_xts, order.by = d_all$datetime)
dygraph(durafet_calc_contros_xts, group = "awipev", main="pH calculated vs pH durafet, normalized at 4°C", ylab="pHT") %>%
    dySeries("pH_durafet_norm4", label = "pH durafet", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_calc_fb_norm4", label = "pH calculated", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
       dyLegend(show = "follow")   %>%
    dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)
```

### **Calculated / seaFET pHs**
```{r pHs comparaison sf calc, echo=FALSE, message= FALSE, warning=FALSE}
seafet_calc_contros_xts <- dplyr::select(d_all, datetime, pHint_tot_sf_norm4, pH_calc_fb_norm4)
seafet_calc_contros_xts <- as.xts(seafet_calc_contros_xts, order.by = d_all$datetime)
dygraph(seafet_calc_contros_xts, group = "awipev", main="pH calculated vs pH seaFET, normalized at 4°C", ylab="pHT") %>%
    dySeries("pHint_tot_sf_norm4", label = "pH seaFET", color ="blue", strokeWidth=0, pointSize=2) %>%
    dySeries("pH_calc_fb_norm4", label = "pH calculated", color =  "red", strokeWidth = 0, pointSize = 4 ) %>%
    # dyOptions(colors = RColorBrewer::brewer.pal(3, "Dark2"), pointSize = 4) %>%
    dyHighlight(highlightCircleSize = 8,highlightSeriesBackgroundAlpha = 0.5,hideOnMouseOut = TRUE) %>%
       dyLegend(show = "follow")   %>%
dyOptions(drawGrid = TRUE, drawPoints = TRUE, pointSize = c(1,8,1),useDataTimezone = TRUE, digitsAfterDecimal=4) %>%
    dyRangeSelector(height = 30, dateWindow= NULL)
```

@@

#### Script awipev-co2.Rmd which runs locally
* reads locally fb_awipev-co2_server/ny-alesund/data/NRT_data/nydata_hour.rds
* sal_mix: when ferrybox data (sal_fb) are missing, they are replaced by data from the profiling ctd for depths > 8 m (sal_insitu_ctd_9m)
* temp_mix: when data of in situ temperature at 11 m (temp_insitu_11m) are missing, they are replaced by data from the profiling ctd for depths > 8 m
* pco2_calc_insitu: pco2 calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
* calibrate seafet pH
    - ph_s_sf_temp_insi: pH spectro seaFET pH insi calculé avec AT interpolée + temp_mix +sal_mix
    - E0int25_sf: calculé à partir du voltage interne + ph_s_sf_temp_insi (temp 11m + temp_insitu_ctd_9m si trous) + temp CTD 9m + sal CTD 9m (calib seaFET fonction 1)
    - phint_tot_sf: calculé à partir du voltage interne + E0 + temp CTD + sal CTD (calib seaFET fonction 2)
* ph_calc: pH calc from AT/CT ferrybox = carb avec temp_fb +sal_fb
* despike pH seaFET
* calibrate durafet pH
    - ph_s_dur_temp_fb: pH spectro durafet pH insi calculé avec AT interpolée + temp_fb +sal_fb
* Relation at / sal_mix 
* at_calc: calculé from sal_mix
* saves locally d_all.rds which comprises all variables plus those generated in the script
